\documentclass[11pt, letterpaper]{article}
\usepackage{afp-style}
\afpdoctype{Ballot Access Petition}

\begin{document}

\afptitlepage{Ballot Access\\Petition Template}{Standardized Petition for Party or Candidate Ballot Access}

\section*{Petition for Ballot Access}

\vspace{0.5em}
{\color{afp-teal}\rule{\textwidth}{0.5pt}}
\vspace{1em}

\formfield[10cm]{State}
\formfield[10cm]{Petition Type ($\square$ Party Recognition \quad $\square$ Candidate Ballot Access)}
\formfield[10cm]{Candidate Name (if applicable)}
\formfield[10cm]{Office Sought (if applicable)}
\formfield[6cm]{Election Date}
\formfield[6cm]{Filing Deadline}
\formfield[6cm]{Required Signatures}

\section{Petition Statement}

We, the undersigned registered voters of the State of \rule{4cm}{0.4pt}, do hereby petition for:

\vspace{0.5em}
\noindent
\begin{tabular}{@{}l@{}}
$\square$ \quad Recognition of the Anti-Federalist Party as a qualified political party. \\[0.5em]
$\square$ \quad Placement of the named candidate on the official ballot. \\
\end{tabular}

\vspace{1em}

We affirm that each signer is a duly registered voter of this state and that each signature was affixed voluntarily.

\section{Petition Signatures}

\afpcallout{Each page must contain the circulator's affidavit. Verify your state's requirements for format, county grouping, and notarization before collecting signatures.}

\vspace{0.5em}
\begin{center}
\begin{tabularx}{\textwidth}{|c|X|X|X|X|}
\hline
\rowcolor{afp-teal!10}
\textbf{\#} & \textbf{Printed Name} & \textbf{Signature} & \textbf{Address} & \textbf{Date} \\
\hline
1 & & & & \\[0.9cm] \hline
2 & & & & \\[0.9cm] \hline
3 & & & & \\[0.9cm] \hline
4 & & & & \\[0.9cm] \hline
5 & & & & \\[0.9cm] \hline
6 & & & & \\[0.9cm] \hline
7 & & & & \\[0.9cm] \hline
8 & & & & \\[0.9cm] \hline
9 & & & & \\[0.9cm] \hline
10 & & & & \\[0.9cm] \hline
\end{tabularx}
\end{center}

\section{Circulator Affidavit}

I, \rule{6cm}{0.4pt}, being duly sworn, state that:

\begin{enumerate}
  \item I am a resident of the State of \rule{4cm}{0.4pt}.
  \item I personally witnessed each signature on this petition sheet.
  \item Each person who signed this petition did so voluntarily and of their own free will.
  \item I have not offered any compensation or consideration in exchange for any signature.
  \item To the best of my knowledge, each signer is a registered voter of this state.
\end{enumerate}

\signatureline{Circulator Signature}

\formfield[10cm]{Circulator Printed Name}
\formfield[10cm]{Circulator Address}

\subsection{Notarization}

\afpcallout{Some states require notarization of the circulator affidavit. Check your state's requirements before submitting.}

\noindent State of \rule{4cm}{0.4pt}, County of \rule{4cm}{0.4pt}

\vspace{0.5em}
\noindent Subscribed and sworn to before me this \rule{2cm}{0.4pt} day of \rule{3cm}{0.4pt}, 20\rule{1cm}{0.4pt}.

\signatureline{Notary Public}

\formfield[6cm]{Commission Expires}

\noindent [NOTARY SEAL]

\newpage

\afpcertification{Ballot Access Petition}

\vspace{1.5cm}

\begin{center}
  {\small\color{afp-gray}\sffamily
    This template must be adapted to comply with your state's specific\\
    petition format requirements. Consult your state election authority.\\[0.5em]
    \texttt{anti-federalists.com/documents/states}
  }
\end{center}

\end{document}
