\documentclass[11pt, letterpaper]{article}
\usepackage{afp-style}
\afpdoctype{Chapter Charter}

\begin{document}

\afptitlepage{Chapter Charter}{Template for Local Chapter Activation}

\section*{Declaration of Chapter Formation}

We, the undersigned founding members, hereby establish a local chapter of The Anti-Federalist Party in accordance with Article~IV of the Party Constitution. By executing this Charter, we affirm our commitment to the Principles of the Party and our intent to practice the decentralized, community-driven governance we advocate.

\vspace{1.5em}
\begin{center}
{\color{afp-teal}\rule{8cm}{0.5pt}}
\end{center}
\vspace{1em}

\section{Chapter Identification}

\formfield[10cm]{Official Chapter Name}
\formfield[10cm]{Geographic Jurisdiction (County / Municipality)}
\formfield[6cm]{State}
\formfield[6cm]{Date of Formation}

\section{Founding Members}

A minimum of five (5) founding members is required to establish a chapter.

\vspace{0.5em}
\begin{center}
\begin{tabularx}{\textwidth}{|c|X|X|X|}
\hline
\rowcolor{afp-teal!10}
\textbf{\#} & \textbf{Full Name} & \textbf{Signature} & \textbf{Date} \\
\hline
1 & & & \\[1cm] \hline
2 & & & \\[1cm] \hline
3 & & & \\[1cm] \hline
4 & & & \\[1cm] \hline
5 & & & \\[1cm] \hline
6 & & & \\[1cm] \hline
7 & & & \\[1cm] \hline
8 & & & \\[1cm] \hline
\end{tabularx}
\end{center}

\section{Initial Officers}

The following officers have been elected by the founding members at the organizational meeting:

\vspace{0.5em}
\formfield[10cm]{Chair}
\formfield[10cm]{Vice Chair}
\formfield[10cm]{Secretary}
\formfield[10cm]{Treasurer}

\section{Affirmation of Principles}

By signing this Charter, each founding member affirms:

\begin{enumerate}
  \item Adherence to the Principles set forth in Article~II of the Party Constitution.
  \item Commitment to transparent, democratic governance within the chapter.
  \item Refusal to accept corporate PAC money or donations that create quid pro quo obligations.
  \item Commitment to holding a minimum of four (4) meetings per year.
  \item Commitment to maintaining financial records open to inspection by any member.
\end{enumerate}

\section{Operating Agreements}

\subsection{Meeting Schedule}
\formfield[10cm]{Regular Meeting Day/Time (e.g., ``First Tuesday, 7:00 PM'')}
\formfield[10cm]{Meeting Location or Virtual Platform}

\subsection{Dues}
\formfield[6cm]{Monthly/Annual Dues Amount (or ``None'')}

\subsection{Communication}
\formfield[10cm]{Primary Communication Channel (email list, Signal group, etc.)}

\section{Submission}

This Charter shall be submitted to the Anti-Federalist Party national registry at \texttt{chapters@anti-federalists.com} along with:

\begin{itemize}
  \item A copy of this signed Charter.
  \item Contact information for the Chair and Secretary.
  \item A brief description of the chapter's geographic jurisdiction.
\end{itemize}

\afpcallout{Upon receipt and verification, the national registry will confirm charter status within thirty (30) days. Charter status grants the chapter full voting rights at the National Convention and access to shared Party resources.}

\newpage

\afpcertification{Charter Certification}

\vspace{2.5cm}

\signatureline{Chapter Chair}

\signatureline{Chapter Secretary}

\signatureline{Witness / Founding Member}

\vspace{2cm}

\begin{center}
  {\small\color{afp-gray}\sffamily
    This Charter was duly executed by the founding members listed herein.\\[0.5em]
    Submit signed original to \texttt{chapters@anti-federalists.com}
  }
\end{center}

\end{document}
