\documentclass[11pt, letterpaper]{article}
\usepackage{afp-style}
\afpdoctype{State Formation Packet}

\begin{document}

\afptitlepage{State Party\\Formation Packet}{Official Filing Documentation for State-Level Recognition}

\tableofcontents
\newpage

\section{Overview}

This packet contains all documentation required to formally establish a state-level organization of the Anti-Federalist Party. Each state has different requirements for political party recognition. This standardized packet provides the core documentation needed regardless of jurisdiction.

\afpcallout{Before proceeding, consult the state-specific requirements guide at \texttt{anti-federalists.com/documents/states}. Filing requirements, deadlines, and signature thresholds vary significantly by state.}

\section{Statement of Organization}

\formfield[10cm]{State}
\formfield[10cm]{Official Party Name (``Anti-Federalist Party of [State]'')}
\formfield[10cm]{Date of Organization}
\formfield[10cm]{State Party Headquarters Address}
\formfield[10cm]{Mailing Address (if different)}

\subsection{Principal Officers}

\formfield[10cm]{State Chair}
\formfield[10cm]{State Vice Chair}
\formfield[10cm]{State Secretary}
\formfield[10cm]{State Treasurer}
\formfield[10cm]{Designated Agent for Service of Process}

\subsection{Contact Information}

\formfield[10cm]{Official Email}
\formfield[6cm]{Official Phone}
\formfield[10cm]{Website}

\section{Statement of Purpose}

The Anti-Federalist Party of \rule{4cm}{0.4pt} is organized for the purpose of:

\begin{enumerate}
  \item Nominating and supporting candidates for public office at the local, county, state, and federal levels within the State of \rule{4cm}{0.4pt}.
  \item Advancing the principles of decentralized governance, individual sovereignty, and community self-determination.
  \item Educating the electorate on the Anti-Federalist intellectual tradition and its application to contemporary governance.
  \item Providing an alternative to the two-party monopoly that currently dominates political life in this state.
\end{enumerate}

\section{Adopted Principles}

The Anti-Federalist Party of \rule{4cm}{0.4pt} hereby adopts and affirms the Principles of the Anti-Federalist Party as set forth in Article~II of the national Party Constitution, including:

\begin{enumerate}
  \item \textbf{Decentralization of Power} --- Political authority derives from individuals and communities.
  \item \textbf{Individual Sovereignty} --- Inherent, inalienable rights that no government may abridge.
  \item \textbf{Community Self-Determination} --- Communities have the right to govern themselves.
  \item \textbf{Separation of Corporate and State Power} --- No corporate preferential treatment.
  \item \textbf{Fiscal Responsibility} --- No generational debt without consent.
  \item \textbf{Transparency and Accountability} --- All government operations must be transparent.
  \item \textbf{Non-Interventionism} --- The military exists to defend American soil.
\end{enumerate}

\section{Financial Disclosure}

\formfield[10cm]{Bank Name and Branch}
\formfield[6cm]{Account Number (last 4 digits)}
\formfield[10cm]{Authorized Signatories}

\subsection{Financial Compliance}

The Anti-Federalist Party of \rule{4cm}{0.4pt} certifies that:

\begin{enumerate}
  \item All contributions and expenditures will be reported in accordance with state campaign finance laws.
  \item The party will not accept corporate donations, PAC contributions, or foreign funding.
  \item The state Treasurer will file all required financial reports with the state election authority.
  \item Complete financial records will be maintained and available for public inspection.
\end{enumerate}

\section{Petition Certification}

\afpcallout{Complete this section only if your state requires a petition for party recognition. Attach the petition sheets as an appendix to this packet.}

\formfield[10cm]{Total Signatures Collected}
\formfield[6cm]{Date Collection Began}
\formfield[6cm]{Date Collection Ended}
\formfield[6cm]{Required Signatures}
\formfield[10cm]{Counties/Districts Represented}

\subsection{Petition Notarization}

I, \rule{6cm}{0.4pt}, do hereby certify under penalty of perjury that all signatures attached to this petition were collected in accordance with the election laws of the State of \rule{4cm}{0.4pt}, that each signer is a registered voter of said state, and that each signature was witnessed by an authorized circulator.

\signatureline{Petition Coordinator}

\section{Convention Certification}

\afpcallout{Complete this section only if your state requires a founding convention for party recognition.}

\formfield[10cm]{Convention Date}
\formfield[10cm]{Convention Location}
\formfield[4cm]{Number of Delegates Present}
\formfield[4cm]{Number of Counties Represented}

\subsection{Convention Actions}

The founding convention of the Anti-Federalist Party of \rule{4cm}{0.4pt} hereby certifies the following actions:

\begin{enumerate}
  \item Adoption of the National Party Constitution as the governing document of the state party.
  \item Election of state officers as listed in Section~2 of this packet.
  \item Adoption of state-specific bylaws (attached).
  \item Authorization of the State Chair to file this Statement of Organization with the appropriate state election authority.
\end{enumerate}

\signatureline{Convention Presiding Officer}

\signatureline{Convention Secretary}

\newpage

\section{Submission Checklist}

Before submitting this packet to your state election authority, verify:

\noindent
\begin{tabular}{@{}l@{}}
$\square$ \quad Statement of Organization complete with all officer information \\[0.5em]
$\square$ \quad Statement of Purpose signed \\[0.5em]
$\square$ \quad Principles adopted and affirmed \\[0.5em]
$\square$ \quad Financial disclosure complete \\[0.5em]
$\square$ \quad Petition sheets attached (if applicable) \\[0.5em]
$\square$ \quad Convention minutes attached (if applicable) \\[0.5em]
$\square$ \quad State Committee Bylaws attached \\[0.5em]
$\square$ \quad Filing fee enclosed (if applicable) \\[0.5em]
$\square$ \quad Copy retained for state party records \\[0.5em]
$\square$ \quad Copy sent to national registry at \texttt{states@anti-federalists.com} \\
\end{tabular}

\newpage

\afpcertification{State Party Formation Packet}

\vspace{2.5cm}

\signatureline{State Chair}

\signatureline{State Secretary}

\signatureline{State Treasurer}

\vspace{2cm}

\begin{center}
  {\small\color{afp-gray}\sffamily
    Filed with the election authority of the State of \rule{4cm}{0.4pt}\\[0.5em]
    Copy submitted to Anti-Federalist Party national registry\\[0.25em]
    \texttt{anti-federalists.com}
  }
\end{center}

\end{document}
